State-Space Model to Estimate Salmon Escapement Using Multiple Data Sources

### 2020-08-07 analysis/paper/paper.Rmd
changed the link for NAJFM, put in pdf figure width default (single column), and changed table headers to only have first word capitalized (per NAJFM instructions).

---
title: "State-Space Model to Estimate Salmon Escapement Using Multiple Data Sources"
author:
  - Kevin E. See:
      email: Kevin.See@merck.com
      institute: [BM]
      correspondence: true
  - Ryan N. Kinzer:
      email: ryank@nezperce.org
      institute: [NezPerce]
      correspondence: false
  - Mike W. Ackerman:
      email: mike.ackerman@merck.com
      institute: [BM]
      correspondence: false
institute:
  - BM: Biomark, Inc. 705 South 8th St., Boise, Idaho, 83702, USA
  - NezPerce: Nez Perce Tribe, Department of Fisheries Resource Management, 14054 Burr Road, PO Box 1942, McCall, Idaho, 83638, USA
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
    bookdown::html_document2:
      fig_caption: yes
      number_sections: FALSE
      toc: no
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::pdf_document2:
      fig_caption: yes
      number_sections: FALSE
      toc: no
      geometry: margin=1in
      latex_engine: "xelatex"
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks2.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      number_sections: FALSE
      toc: no
      always_allow_html: true
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
fontsize: 12pt
mainfont: Times New Roman
bibliography:
- references.bib
- packages.bib
csl: "../templates/american-fisheries-society.csl" # Insert path for the bib-style
abstract: |
  This is the abstract
keywords: |
  escapement; Chinook; steelhead; Lower Granite Dam; state-space model; Bayesian model
highlights: |
  These are the highlights. 
---

@@

* **[North American Journal of Fisheries](http://www.tandfonline.com/action/journalInformation?show=aimsScope&journalCode=ujfm20)**

@@

```{r lgr-sim-tab}
crossing(`Trap Rate` = c('0.15', 
                         "0.15 and 0.00 3 weeks"),
         `Fallback Rate` = c(0.06,
                             0.10),
         `Re-ascension Rate` = 1,
         `Window Count Error` = factor(c("No Error",
                                         "10% Error",
                                         "5% Error"),
                                       levels = c("No Error",
                                                  "10% Error",
                                                  "5% Error"))) %>%
  mutate(`Nighttime Passage Rate` = if_else(`Fallback Rate` == 0.06,
                                            0.06,
                                            0.05)) %>%
  mutate(Scenario = paste(rep(c('Baseline',
                                "N-R",
                                "N-R Trap Down",
                                "Trap Down"),
                              each = 3),
                          c("",
                            "Err H", 
                            "Err L"))) %>%
  select(Scenario, 
         `Trap Rate`:`Re-ascension Rate`,
         `Nighttime Passage Rate`,
         `Window Count Error`) %>%
  kable(digits = 2,
        booktabs = T,
        caption = "Summary of simulation scenarios including varying adult trapping, fallback rates, re-ascension, nighttime passage, and window count error rates use to evaluate the performance of STADEM.") %>%
  kable_styling()

@@

```{r summ-tab}
sum_tab <- res_long_df %>%
  filter(Variable == 'Unique.Wild.Fish',
         Model == 'STADEM') %>%
  group_by(Scenario) %>%
  summarise(inCI = sum(inCI),
            nsims = n(),
            Sample_Mean = mean(est),
            `Relative Bias` = mean(rel_bias),
            SE = sqrt(var(est)),
            `Mean CV` = mean(cv),
            RMSD = sqrt(var(est) + mean(bias)^2),
            Coverage = inCI/nsims) %>%
  mutate(Scenario = str_replace_all(Scenario,
                                    "_", " "),
         Scenario = str_replace(Scenario,
                                "TrapDown",
                                "Trap Down")) %>%
  select(Scenario,
         `Relative Bias`,
         `Mean CV`,
         RMSD,
         Coverage)

@@

```{r lgr-tab}
lgr_est %>%
  mutate(prnt_val = if_else(is.na(cv),
                            as.character(prettyNum(round(mean), big.mark = ',')),
                            paste0(prettyNum(round(mean), big.mark = ","), " (", round(cv, 3), ")"))) %>%
  pivot_wider(id_cols = c("Species",
                          "Year"),
              names_from = "variable",
              values_from = "prnt_val") %>%
  select(Species, 
         Year,
         `Window Counts` = win_cnt,
         Total = X.tot.new.all,
         Wild = X.tot.new.wild,
         Hatchery = X.tot.new.hatch,
         `Hatchery No-Clip` = X.tot.new.hnc) %>%
  kable(booktabs = T,
        caption = "Window counts, and estimates of total, wild, hatchery and hatchery no-clip escapement, with coefficients of variation in parenthesis, for Chinook salmon and steelhead from spawn years 2010 to 2019.") %>%
  kable_styling()
```

>>>>

---
title: "State-Space Model to Estimate Salmon Escapement Using Multiple Data Sources"
author:
  - Kevin E. See:
      email: Kevin.See@merck.com
      institute: [BM]
      correspondence: true
  - Ryan N. Kinzer:
      email: ryank@nezperce.org
      institute: [NezPerce]
      correspondence: false
  - Mike W. Ackerman:
      email: mike.ackerman@merck.com
      institute: [BM]
      correspondence: false
institute:
  - BM: Biomark, Inc. 705 South 8th St., Boise, Idaho, 83702, USA
  - NezPerce: Nez Perce Tribe, Department of Fisheries Resource Management, 14054 Burr Road, PO Box 1942, McCall, Idaho, 83638, USA
date: "`r format(Sys.time(), '%B %d, %Y')`"
output:
    bookdown::html_document2:
      fig_caption: yes
      number_sections: FALSE
      toc: no
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::pdf_document2:
      fig_caption: yes
      number_sections: FALSE
      toc: no
      geometry: margin=1in
      latex_engine: "xelatex"
      fig_width: 3.5
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks2.lua
      - --lua-filter=../templates/pagebreak.lua
    bookdown::word_document2:
      fig_caption: yes
      reference_docx: "../templates/template.docx" # Insert path for the DOCX file
      number_sections: FALSE
      toc: no
      always_allow_html: true
      pandoc_args:
      - --lua-filter=../templates/scholarly-metadata.lua
      - --lua-filter=../templates/author-info-blocks.lua
      - --lua-filter=../templates/pagebreak.lua
fontsize: 12pt
mainfont: Times New Roman
bibliography:
- references.bib
- packages.bib
csl: "../templates/american-fisheries-society.csl" # Insert path for the bib-style
abstract: |
  This is the abstract
keywords: |
  escapement; Chinook; steelhead; Lower Granite Dam; state-space model; Bayesian model
highlights: |
  These are the highlights. 
---

@@

* **[North American Journal of Fisheries](https://afspubs.onlinelibrary.wiley.com/journal/15488675)**

@@

```{r lgr-sim-tab}
crossing(`Trap rate` = c('0.15', 
                         "0.15 and 0.00 3 weeks"),
         `Fallback rate` = c(0.06,
                             0.10),
         `Re-ascension rate` = 1,
         `Window count error` = factor(c("No Error",
                                         "10% Error",
                                         "5% Error"),
                                       levels = c("No Error",
                                                  "10% Error",
                                                  "5% Error"))) %>%
  mutate(`Nighttime passage rate` = if_else(`Fallback rate` == 0.06,
                                            0.06,
                                            0.05)) %>%
  mutate(Scenario = paste(rep(c('Baseline',
                                "N-R",
                                "N-R trap down",
                                "Trap down"),
                              each = 3),
                          c("",
                            "Err H", 
                            "Err L"))) %>%
  select(Scenario, 
         `Trap rate`:`Re-ascension rate`,
         `Nighttime passage rate`,
         `Window count error`) %>%
  kable(digits = 2,
        booktabs = T,
        caption = "Summary of simulation scenarios including varying adult trapping, fallback rates, re-ascension, nighttime passage, and window count error rates use to evaluate the performance of STADEM.") %>%
  kable_styling()

@@

```{r summ-tab}
sum_tab <- res_long_df %>%
  filter(Variable == 'Unique.Wild.Fish',
         Model == 'STADEM') %>%
  group_by(Scenario) %>%
  summarise(inCI = sum(inCI),
            nsims = n(),
            Sample_Mean = mean(est),
            `Relative bias` = mean(rel_bias),
            SE = sqrt(var(est)),
            `Mean CV` = mean(cv),
            RMSD = sqrt(var(est) + mean(bias)^2),
            Coverage = inCI/nsims) %>%
  mutate(Scenario = str_replace_all(Scenario,
                                    "_", " "),
         Scenario = str_replace(Scenario,
                                "TrapDown",
                                "Trap Down")) %>%
  select(Scenario,
         `Relative bias`,
         `Mean CV`,
         RMSD,
         Coverage)

@@

```{r lgr-tab}
lgr_est %>%
  mutate(prnt_val = if_else(is.na(cv),
                            as.character(prettyNum(round(mean), big.mark = ',')),
                            paste0(prettyNum(round(mean), big.mark = ","), " (", round(cv, 3), ")"))) %>%
  pivot_wider(id_cols = c("Species",
                          "Year"),
              names_from = "variable",
              values_from = "prnt_val") %>%
  select(Species, 
         Year,
         `Window counts` = win_cnt,
         Total = X.tot.new.all,
         Wild = X.tot.new.wild,
         Hatchery = X.tot.new.hatch,
         `Hatchery no-clip` = X.tot.new.hnc) %>%
  kable(booktabs = T,
        caption = "Window counts, and estimates of total, wild, hatchery and hatchery no-clip escapement, with coefficients of variation in parenthesis, for Chinook salmon and steelhead from spawn years 2010 to 2019.") %>%
  kable_styling()
```
